---
title: "P8105 Homework 1"
author: JingYao Geng
output: github_document
---

This is my solution to HW1 


## Preparation: 

##### Load the package 'tidyverse'
```{r access library, message = FALSE}
library(tidyverse)
```


## Problem 1

##### a)  Create a data frame with the specified elements

```{r prob1_df: create df, collapse = TRUE}
# Create and define the data frame
prob1_df = 
  tibble(
    samp = rnorm(n = 10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h","i","j" ),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
# Take a look at 'prob1_df' 
prob1_df
```


##### b)  Take the mean of each variable in the data frame

```{r prob1_df: mean_pull_var, message = FALSE, collapse = TRUE}
# pull out the variables and take the mean for each of them

mean(pull(prob1_df, samp))        # mean of the numeric 

mean(pull(prob1_df, samp_gt_0))   # mean of the logical 

mean(pull(prob1_df, char_vec))    # mean of the character 

mean(pull(prob1_df, factor_vec))  # mean of the factor
```

I can take the mean of numbers and logical but not character or factor variables.


##### c)  Convert the logical, character, and factor variables into numeric variable

```{r prob1_df: try_num, eval=FALSE}
# Apply the as.numeric function

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


##### d)  Convert the logical vector to numeric, factor, and multiply the random sample by the result

```{r prob1_df: multiply, collapse = TRUE}
# logical -> numeric, and multiply the random sample
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor, and multiply the random sample
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor -> numeric, and multiply the random samp 
as.numeric(as.factor(pull(prob1_df, factor_vec))) * pull(prob1_df, samp)
```

# Problem 2

