---
title: "P8105 Homework 1"
author: JingYao Geng
output: github_document
---

> This is my solution to HW1


##### Load the package 'tidyverse'

```{r access_lib, message = FALSE}
library(tidyverse)

```


## Problem 1

##### a)  Create a data frame with the specified elements

```{r prob1_df: create df, collapse = TRUE}
# Create and define the data frame
prob1_df = 
  tibble(
    samp = rnorm(n = 10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h","i","j" ),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
# Take a look at 'prob1_df' 
prob1_df
```


##### b)  Take the mean of each variable in the data frame

```{r prob1_df: mean_pull_var, message = FALSE, collapse = TRUE}
# pull out the variables and take the mean for each of them

mean(pull(prob1_df, samp))        # mean of the numeric 

mean(pull(prob1_df, samp_gt_0))   # mean of the logical 

mean(pull(prob1_df, char_vec))    # mean of the character 

mean(pull(prob1_df, factor_vec))  # mean of the factor
```

I can take the mean of numbers and logical but not character or factor variables.


##### c)  Convert the logical, character, and factor variables into numeric variable

```{r prob1_df: try_num, eval=FALSE}
# Apply the as.numeric function

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


##### d)  Convert the logical vector to numeric, factor, and multiply the random sample by the result

```{r prob1_df: multiply, collapse = TRUE}
# logical -> numeric, and multiply the random sample
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor, and multiply the random sample
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor -> numeric, and multiply the random samp 
as.numeric(as.factor(pull(prob1_df, factor_vec))) * pull(prob1_df, samp)
```

## Problem 2

#####  a) Load the dataset: _'penguins'_

```{r penguins_ds, collapse = TRUE}
data("penguins", package = "palmerpenguins")
print(penguins) # take a look at the dataset

```


* There are **`r ncol(penguins)`** variables in the **penguins** dataset, they are: "`r names(penguins)`" 
* Among all the variables, 
  * **3** of them are factor: species, island, and sex.
  * **2** of them are doubles: bill length and bill depth.
  * **3** of them are integer: flipper length and body mass.


* The dataset **penguins** has **`r nrow(penguins)`** rows and  **`r ncol(penguins)`** columns. 

* The mean of **flipper length** is  `r summary(penguins$flipper_length_mm)[4]` .


##### b) Scatterplot of flipper_length(y) vs. bill_length_mm(x)

```{r plot, message = FALSE}
plot_fb = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm
)

ggplot(plot_fb, aes(x = x, y = y)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
