---
title: "P8105 Homework 1"
author: JingYao Geng
output: github_document
---

> This is my solution to HW1

```{r access_lib, message = FALSE}
library(tidyverse) # load the package

```


## Problem 1

##### a)  Create a data frame with the specified elements

```{r prob1_df: create df, collapse = TRUE}
# Create and define the data frame
prob1_df = 
  tibble(
    samp = rnorm(n = 10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h","i","j" ),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
# Take a look at 'prob1_df' 
prob1_df
```


##### b)  Take the mean of each variable in the data frame

```{r prob1_df: mean_pull_var, message = FALSE, collapse = TRUE}
# pull out the variables and take the mean for each of them

mean(pull(prob1_df, samp))        # mean of the numeric 

mean(pull(prob1_df, samp_gt_0))   # mean of the logical 

mean(pull(prob1_df, char_vec))    # mean of the character 

mean(pull(prob1_df, factor_vec))  # mean of the factor
```

I can take the mean of numbers and logical but not character or factor variables.


##### c)  Convert the logical, character, and factor variables into numeric variable

```{r prob1_df: try_num, eval=FALSE}
# Apply the as.numeric function

as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


##### d)  Convert the logical vector to numeric, factor, and multiply the random sample by the result

```{r prob1_df: multiply, collapse = TRUE}
# logical -> numeric, and multiply the random sample
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor, and multiply the random sample
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)

# logical -> factor -> numeric, and multiply the random samp 
as.numeric(as.factor(pull(prob1_df, factor_vec))) * pull(prob1_df, samp)
```

## Problem 2

#####  a) Load the dataset: _'penguins'_

```{r penguins_ds, collapse = TRUE}
data("penguins", package = "palmerpenguins")

```

A short description of penguins:

There are **`r ncol(penguins)`** variables in the **penguins** dataset, they are: "`r names(penguins)`" .

Among all the variables, 

* **3** of them are factor: species, island, and sex.
  * The levels of species are: `r levels(pull(penguins,species))`. 
  * The levels of islands are: `r levels(pull(penguins,island))`.
  * The levels of sex are: `r levels(pull(penguins,sex))`. 
  
* **2** of them are doubles: bill length and bill depth.
  * The range of bill length is `r range(pull(penguins, bill_length_mm),na.rm=T)`mm. 

  * The range of bill depth is `r range(pull(penguins, bill_depth_mm),na.rm=T)`mm.
  
* **3** of them are integer: flipper length, body mass, and year.
  * The range of flipper length is `r range(pull(penguins, flipper_length_mm),na.rm=T)`mm.
  * The range of body mass is `r range(pull(penguins,     body_mass_g),na.rm=T)`g. 


The dataset **penguins** has **`r nrow(penguins)`** rows and  **`r ncol(penguins)`** columns. 

The mean of **flipper length** is  **`r summary(penguins$flipper_length_mm)[4]`** .


##### b) Scatterplot of flipper_length(y) vs. bill_length_mm(x)

```{r plot, message = FALSE, collapse = TRUE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)# save as a pdf
```
